\begin{abstract} Recent episodes of governments' attempts to access user data
have drawn increased concern to where data belonging to or about a user
(including a user's access patterns) is located. The location of user data
can affect which governing authorities can access it. Because Content
Distribution Networks (CDNs) can cache content in many different countries,
often without regard to the owner of the data, a user's data may reside in a
country that differs from their own. Many  battles over stored data privacy
have played out in the courts, with legal opinions rendering essentially
ambiguous outcomes thus far. This paper offers a technical contribution to
this tussle. We first analyze the privacy  issues a CDN faces in the presence
of a government (or insider) who would wish to access information about what
data is being stored on the CDN and who is accessing it. To mitigate the
resulting threats, we design and implement \system{}, a system provides {\em
oblivious content distribution}, a property that allows CDNs to provide the
performance benefits of content distribution and caching, while preventing the
CDN from knowing what content that is stored on the CDN or who is accessing
it. These properties of \system{} provide protections for both the client, the
content owner, and the CDN operator. We design a the protocol for publishing
retrieving content using \system{} and, through a prototype implementation and
evaluation, show that the performance overhead is negligible.
\end{abstract}
