\section{Introduction}
\label{sec:intro}

As Content Distribution Networks (CDNs) host more content,
they are fast becoming targets of requests for information about their content
and who is requesting it, as well as requests for takedown of material ranging
from alleged copyright violations to offensive content. The shifting legal and
political landscape suggests that CDNs may soon face liability for the content
that they host. For example, the European Union has been considering laws that
would remove safe harbor protection on copyright infringement for online
service providers if they do not deploy tools that can automatically inspect
and remove infringing content~\cite{eu-copyright}. In the United States,
various laws under consideration threaten aspects of Section 230 of the
Communications Decency Act~\cite{sec230}, which protects CDNs from federal
criminal liability for the content that they host. Tussles surrounding speech,
from copyright violations to hate speech, are currently being addressed in the
courts, yet the legal outcomes remain ambiguous and uncertain, sometimes with
courts issuing opposing rulings in different cases. Regardless of these
outcomes, however, CDNs are increasingly in need of {\em technical}
protections against the liability they might face as a result of content that
they (perhaps unwittingly) serve.

Towards this end, we design and implement a system that allows clients to
retrieve web objects from one or more CDNs, while preventing the CDNs from
learning either (1)~the content that is stored on the cache nodes; or (2)~the content
that clients request, and the clients that request it. We call this system an {\em
oblivious
CDN}~(\system{}), because the CDN is oblivious to both the content it is
storing and the content that clients request.

\system{} allows clients to request objects with identifiers that
are encrypted with a key that is shared by an open proxy and the origin server
that publishes content to cache nodes, but is not known to any of the CDN
cache nodes.  To do so, the origin server publishes encrypted content, 
which the CDN cache nodes subsequently share with one or more proxies that are responsible
for
routing requests for objects corresponding to that URL.  A client forwards a
request for content through other OCDN clients in a way
that prevents both other clients and the CDN from learning the client
identity or requested content.  Using \system{} requires only minimal modification to existing clients; clients can also configure aspects of the system to trade off performance for privacy.

Ensuring that the CDN operator never learns information about either (1)~what
content is being stored on its cache nodes or (2)~which objects individual
clients are requesting is challenging, due to the many possible inference
attacks that a CDN might be able to mount. For example, previous work has
shown that even when web content is encrypted, the retrieval of a collection
of objects of various sizes can yield information about the web page that was
being retrieved~\cite{panchenko2016website, cai2012touching}. Similarly, URLs
can often be inferred from relative popularity in a distribution of web
requests, even when the requests themselves are encrypted. Additionally, the
\system{} design assumes a strong attack model (Section~\ref{sec:threat}),
whereby an adversary can request logs from the CDN, interact with \system{} as
a client, a proxy, or a publisher, and mount coordinated attacks that depend on
multiple such capabilities. Our threat model does not include active attempts
to disrupt the system (\eg, blocking access to parts of the system, mounting
denial of service attacks), but it includes any type of attack
that involves observing traffic and even directly interacting with the system
as a client, proxy, or publisher.

The rest of this paper is structured as follows. We provide a brief background
of CDNs, privacy implications, and legal questions in
Section~\ref{sec:background}. We discuss the threat model in
Section~\ref{sec:threat}. In Section~\ref{sec:design}, we detail the design of
\system{}. We describe our process for obfuscating requests and content in
Section~\ref{sec:protocol}.  
Section~\ref{sec:implementation} describes our prototype implementation. Section~\ref{sec:performance}
studies the performance implications of the tradeoffs between performance and
privacy, as well as how \system{} performs relative to a conventional CDN. Section~
\ref{sec:sec} analyzes how \system{}
defends against threats from our adversary.
Section~\ref{sec:discussion} describes various limitations and possible
avenues for future work, Section~\ref{sec:related} discusses related work, and
Section~\ref{sec:conclusion} concludes.

\if 0
While government access of data at a CDN could compromise a client's privacy,
it becomes a more complex issue when the data being cached is geographically
distributed. This is clearly illustrated in the following example.  There is a
content publisher in  country X, and she's a customer of a CDN, so her content
is replicated at cache nodes in many  different countries.  The CDN is
headquartered  in country Y and operates cache nodes around the world.  In
this scenario it is not clear which government can ask the CDN for
information; for  example, a government adversary may wish to learn the
identity of the owner of the content, or which clients are accessing  this
content.  Country X could demand the information of the CDN by arguing that
the content is originating  from their country; Country Y could argue for the
access to the data by stating that the CDN falls under their  law.  Lastly,
another country may request the information because the content is replicated
and stored within  their country.  The fact that CDNs distribute content and
store it around the world opens the possibility of  many governments demanding
access to publisher and client information.

The stakeholders in this example are the content publisher, the CDN, and the
Internet users --- and each of these entities differ in what  they have at
stake.  Alice may be punished for publishing controversial content (such as
content that  goes against the current regime); the CDN  may be held liable
for controversial information (or copyright infringing content); the Internet
users'  privacy could be leaked.  Each stakeholder should be interested (and
possibly worried) about the  consequences of overreaching government access.
\system{} is a novel design that allows technologists to play  a role in the
way data is governed, and to protect users, operators, and publishers from an
overreaching government (or  conflicting jurisdictional policies).
\fi 
