\section{OCDN Threats and Goals}
\label{sec:threat}
In this section, we describe our threat model, outline the capabilities of the 
attacker, and introduce the design goals and protections that \system{} provides.

\subsection{Threat Model}
\label{sec:attacker}

Our threat model concerns a powerful adversary who has a variety of capabilities,
including both surveilling network traffic, inferring user activities, and joining
the system in various capacities.
We assume that an adversary can gain
access to the CDNs logs, which typically contains client IP addresses and URLs for
each request, both indirectly through traffic observation or directly with a data
request. Additionally,
the adversary could join \system{} as either a single client or multiple clients,
or by running an arbitrary number of \system{} proxies.  The adversary could 
also act as an origin server (a content publisher), or multiple independent content
publishers. We also assume that the adversary
can coordinate several of these actions to learn more information.  For example, the 
adversary could join as a client and proxy, and request access to the CDN's
logs to observe how its own requests are obfuscated.  Additionally, 
the adversary can perform actions, such as generating requests as a client, or creating content 
as a content publisher. We assume that an adversary could perform any combination
of the above attacks in an attempt to learn about either (1)~the content being stored
at the CDN or (2)~which clients are accessing which content.  

The strong adversary that is a real adversary that has emerged in practice:
for example, governments have demanded access to CDNs'
data~\cite{cloudflare_nsl}.  Although one possible adversary is a government
requesting logs from the CDN,  the government could also be colluding with a
CDN; we also consider that the CDN operator \textit{itself} can be considered an adversary.

Our design does not defend against an attacker who attempts to actively
disrupt or block access to the system, such as by actively modifying content,
disrupting communications (\eg, through denial of service), or blocking
access, content, or requests. Previous work on securing CDNs has introduced
methods to handle an actively malicious adversary by preserving the integrity
of content  stored on CDN cache nodes~\cite{levy2015stickler} and could be
deployed in conjunction with \system{}. We do not address an adversary that
tampers, modifies, or deletes any data, content, or requests.  In addition, we
do not consider an omniscient adversary that can globally, passively monitor
all Internet traffic; for example, \system{} cannot defend against an attacker
who can see all incoming and outgoing messages from all clients and proxies.

\subsection{Security and Privacy Goals}
\label{sec:goals}

To defend against the adversary described in Section~\ref{sec:attacker}, we
highlight the design goals for \system{}.  Each stakeholder---in this case,
the content publisher, the CDN, and the client---has different risks, and
therefore should have different protections.  All three stakeholders  can be
protected by preventing CDNs from learning information, decoupling content
distribution from trust, and  maintaining the performance benefits of a CDN
while reducing the probability of attacks.   One strength of \system{} is that
it protects the origin server, the CDN itself, and the client, whereas
existing systems, such as Tor, only protect the client.


\subsubsection{Prevent the CDN from knowing the content it is caching.} \label{sec:contentgoal}
First and foremost, the CDN 
should not have access to the information outlined 
in Section~\ref{sec:background}.  By limiting the information that the CDN knows,
\system{} limits 
the amount of information that an adversary can learn or request. \system{} should hide 
the content as well as the URL associated with the content.  If the CDN 
does not know what content it is caching, then the CDN will not be able to supply an adversary 
with the requested data and it will have a strong argument as to why it cannot be held 
liable for its customers' content.

\subsubsection{Prevent the CDN from knowing the identity of users accessing content.} \label{sec:usergoal}
CDNs can currently see clients' 
browsing patterns. \system{} should provide privacy protections by hiding which client is accessing 
which content at the CDN.  In addition, it should hide cross-site browsing patterns,
which a CDN 
is unique in having access to.  Some CDNs block legitimate Tor users because they are 
trying to protect cached content from attacks, such as comment spam, vulnerability scanning, 
ad click fraud, content scraping, and login scanning~\cite{ars_tor}; for example,
Akamai blocks Tor users~\cite{khattak2016you}. As a positive side effect, \system{}
prevents
privacy-conscious Tor users from being blocked by CDNs.  Finally, some CDNs, due
to their ability
to view cross site browsing patterns, could de-anonymize Tor users~\cite{cloudflare_tor}, but \system{} would 
prevent a CDN from compromising the anonymity of clients.


\subsection{Performance Considerations}
As one of the primary functions of a CDN is to make accessing content faster and more 
reliable, \system{} should consider performance in design decisions.  The performance of \system{} will 
be worse than that of traditional CDNs because it is performing more operations on content, but \system{} 
is offering confidentiality, whereas traditional CDNs are not.  \system{} should scale linearly in terms of load 
and storage requirements on proxies; additionally, it should be able to 
scale with the number of clients using the system, as well as with the growing number of web pages on the internet.

%\begin{table*}[]
%\begin{tabular}{|l|l|l|l|}
%\hline
%                          & \textbf{CDN}                                                               & \textbf{Exit Proxy}                                                                          & \textbf{Transit Proxy}                                                                  \\ \hline
%\textbf{User IP}          & Exit proxy (\cref{sec:hiding_clients})                                                           & Source routing (\cref{sec:hiding_clients})                                                                         & Source routing (\cref{sec:hiding_clients})                                                                    \\ \hline
%\textbf{URL}              & Shared keys (\cref{sec:hiding_content})                                                          & n/a                                                                                          & Session keys (\cref{sec:hiding_clients})                                                                      \\ \hline
%\textbf{Content}          & Shared keys (\cref{sec:hiding_content})                                                          & n/a                                                                                          & Session keys (\cref{sec:hiding_clients})                                                                      \\ \hline
%\textbf{Traffic patterns} & \begin{tabular}[c]{@{}l@{}}Exit proxies\\ Encoding URLs (\cref{sec:enhancements})\end{tabular} & \begin{tabular}[c]{@{}l@{}}Consistent hashing (\cref{sec:hiding_content})\\ Self-certifying IDs (\cref{sec:hiding_content})\end{tabular} & \begin{tabular}[c]{@{}l@{}}Consistent Hashing (\cref{sec:hiding_content})\\ Source routing (\cref{sec:hiding_clients})\end{tabular} \\ \hline
%\end{tabular}
%\caption{OCDN mechanisms for providing privacy goals (row headers) at the various stakeholders (column headers).}
%\label{tab:threats}
%\end{table*}