\section{Data at Rest}
\label{sec:rest}

Data at rest refers to stored data. Bruce Schneier described stored data as a
subset of communications: \say{...a stored message is a way for someone to
communicate with himself through time~\cite{schneier2007applied}.} Although
this characterization is valid in an abstract, in practice the measures needed
to protect the privacy of both types of data are quite different.  An example
of data at rest is a database of credit card information associated with a
website. This information is stored on some machine and is accessible to
incoming requests. In this section, we discuss some of technical questions
regarding the privacy of data at rest, existing legal precedent, and how (and
why) systems must protect data at rest differently than data in motion.

\subsection{Privacy Questions}  

As with data in motion, encryption cannot fully solve the privacy problems
associated with data at rest.  If stored data is encrypted, then that data
appears to be protected, but in reality the keys used for encrypting the data
are often stored on the same computer or the same network as the data.  In
this case, if the attacker has access to the encrypted data, then he also has
access to the encryption keys, which defeats the entire point of encryption.

A significant difference is that a nation-state adversary not only has the
capability to eavesdrop on data, but also it can in many cases serve an
organization, ISP, or company with a subpoena to access user data: (1)~A
subpeona may be served {\em to an ISP}, which may also have the ability to
man-in-the-middle TLS connections; because the ISP can see the plaintext data
in motion, then it must hand over the requested to data to the nation state,
(2)~A subpoena may be served to a CDN, which may encrypt the data at rest, but
also stores the encryption keys, and {\it can} see the data and which clients
are accessing it, so it must provide the requested data to the nation state.
Technology must protections beyond encryption, especially in the face of a
governments that can gather the data without a user's knowledge, or simply
demand the data.

\subsection{Legal Precedent and Questions}

To put data-at-rest laws into context, we will be focusing on how the United
States governs stored data.  The Stored Communications Act was passed to
prohibit a provider of an electronic communication service ``from knowingly
divulging the contents of any communication while in electronic storage by
that service to any person other then the addressee or intended
recipient''~\cite{stored_comm}.  The law also specifies the type of content
that can be accessed via a subpeona, and addresses National Security Letters
(NSLs).  NSLs allow the Federal Bureau of Investigation (FBI) to compel the
production of subscriber information and electronic communication
transactional records, and the only requirement is that the FBI certifies that
the records sought ``are relevant to an authorized investigation to protect
against international terrorism or clandestine intelligence activities....''
\cite{stored_comm}.  Additionally, each NSL comes with a gag order, which
prevents the electronic service provider from revealing that the data was
requested.

The NSLs provide no transparency regarding what data was demanded, but
fortunately, more and more companies are going public with past NSLs.  In
January 2017, Twitter published two NSLs it received in 2015 and 2016 as the
gag order was lifted; the NSLs required Twitter to hand over the ``name,
address, length of service, and electronic communications transactional
records for all services, as well as all accounts'' pertaining to two
specified accounts~\cite{twitter_gag}.  Twitter is not alone: Yahoo recently
published three NSLs that were previously under gag order and Google published
eight data requests that were under gag order~\cite{yahoo_gag,google_gag}.
More recently, CREDO and Cloudflare have published their respective NSLs; an
on-going court case (CREDO \& Cloudflare v. Jefferson Sessions) has CREDO and
Cloudflare arguing that NSLs violate their freedom of
speech~\cite{cloudflare_gag}.

Many of these companies that have recieved NSLs under gag order have publicly
pushed for more transparency; Google made the statement ``We have fought for
the right to be transparent about our receipt of NSLs. This includes working
with the government to publish statistics about NSLs we’ve received,
successfully fighting NSL gag provisions in court, and leading the effort to
ensure that Internet companies can be more transparent with users about the
volume and scope of national security demands that we receive.'' Along similar
lines, Twitter announced ``Twitter remains unsatisfied with restrictions on
our right to speak more freely about national security requests we may
receive. We would like a meaningful opportunity to challenge government
restrictions when ‘classification’ prevents speech on issues of public
importance.''  Facebook agreed publicly: ``We'll also keep working with
partners in industry and civil society to push governments around the world to
reform surveillance in a way that protects their citizens’ safety and security
while respecting their rights and freedoms''~\cite{cloudflare_gag}.  
Many Internet companies want to protect their customers' data from
government access, yet often lack the technical means to do so.

Microsoft has taken a first step in protecting their customers' privacy.  In
2015, Microsoft established a data center in Germany, which is shepherded by
Deutsche Telekom (Germany's largest telecommunications provider), and
Microsoft will only be given access to the data if either the customer or
Deutsche Telekom's T-Systems subsidiary give
permission~\cite{microsoft_germany}.  This is a first attempt at preventing
U.S. authorities access to the data, and a leading example of how we can use
and develop technology in other ways for this same purpose.

Yet, not all cases side with the user; in April 2017, New
York's highest court ruled that Facebook is not allowed to ask an appellate
court to reject a search warrant ordering them to hand over information from
hundreds of accounts~\cite{facebook_ny}.  Facebook's argument was that the
search warrants were so broad that they were essentially an unconstitutional
search.  This blow to Facebook's attempt at expanding privacy protections for
their users motivates the general need for systems that preserve the privacy
of data at rest.  Additionally, a recent second circuit court case ruled that
Google must turn over emails stored overseas; this effectively has the {\it
opposite} ruling as compared to the Microsoft vs. Ireland case, in which held
that warrants for customer emails are unenforceable when stored on a server
outside the United States~\cite{google_overseas,microsoft_ireland}.

The past few months have also seen a proposal for a United Nations Global
warrant; this would allow the issuing of international surveillance warrants
or international data access warrants (IDAWs) base on international
law~\cite{global_warrant}.  Complementary technology can prevent 
overreach that results in access to broad amounts of data, thus potentially also
resolving ambiguities or laws that are unfavorable towards user privacy.

%[TODO: paragraph on historical case outcomes involving data at rest, reference Microsoft-Ireland Case~\cite{microsoft_ireland} and more recent ruling in Facebook v. New York \cite{facebook_ny}, and discuss what is currently being done, reference Microsoft-Germany data center~\cite{microsoft_germany}]

\subsection{Technical Approaches}
\label{sec:tech_rest}

There has been significantly less work on preserving the privacy of data at
rest from a nation state. Encrypting stored content cannot completely solve
the problem, as a government can order a company to provide certain data, and
currently most companies have both the encrypted content and the encryption
key.  Emerging work may prevent the owner of a content distribution network
from knowing either (1)~which users are requesting which content; or (2)~the content
itself that is being stored on the servers. Such a system could protect the CDN
operator in the face of a subpoena. These systems may also help preserve safe harbor
protections for online service providers in copyright cases, since the design of
the CDN may prevent the operator from being able to discover any of the content
that is hosted on the CDN cache nodes.


%To our knowledge, the only work that has attempted to protect stored data from either a snooping nation state or a nation state which has served a subpoena is ObliviousCDN.  ObliviousCDN is a CDN which is designed to cache content (just as a typical CDN does), but the CDN has know knowledge of the content it is distributing~\cite{edmundson2017cdn}.  It does this by employing proxies between the client and the CDN and ensuring the CDN cache nodes only hold encrypted (or hashed) content.  Unlike the systems discussed in the previous subsection, ObliviousCDN addresses both types of data; it also provides privacy protections for data in motion.  By encrypting content before the data is transferred, and by employing a proxy between the cache node and a set of clients, it provides a level of privacy protection.  


